Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses; consequently, the tool CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results is expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consist of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures, such that the CPA operators can be written in a concise and convenient way~\cite{Beyer2011}. Currently CPAchecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}. The CPA algorithm performs the reachability analysis, and operates on an object of the abstract data type CPA, i.e., the algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing. For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs. In software verification, its usual to take a considerable amount of effort to convert a verification idea into actual experimental results — and CPAchecker aim to accelerate this process~\cite{Beyer2011}.
%
%--------------------------------------------------
\section{Stand-alone PV System Sizing and Verification}
\label{sec:sizingcheck}
%--------------------------------------------------
In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a. sizing check).
%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.

>>>>

The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses; consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results is expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consist of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures, such that the CPA operators can be written in a concise and convenient way~\cite{Beyer2011}. Currently CPAchecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}. The CPA algorithm performs the reachability analysis, and operates on an object of the abstract data type CPA, i.e., the algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing. For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs. In software verification, its usual to take a considerable amount of effort to convert a verification idea into actual experimental results — and CPAchecker aim to accelerate this process~\cite{Beyer2011}.
%
%--------------------------------------------------
\section{Stand-alone PV System Sizing and Verification}
\label{sec:sizingcheck}
%--------------------------------------------------
In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a. sizing check).
%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.
